### 2023-03-12 main/chapter_2ljets.tex
clarify no_sr summary plot differences

\begin{figure}[tp]
\centering
\includegraphics[width=\textwidth]{figures/2ljets_summary_no_sr_log.png}
\caption[
Alternative summary table with backgrounds fitted to control regions only
]{%
Alternative summary table with backgrounds fitted to control regions only.
A version fitted also to signal regions is shown in
Figure~\ref{fig:2ljets_summary}.
Fitting to signal regions is the policy of the \atlas\ SUSY group, but deviates
from the intentions of the significance measure.
Because the post-fit yields in SR-Low achieve a small negative significance,
all mentions of its deficit were removed from the paper.
}
\label{fig:2ljets_summary_no_sr}
\end{figure}

>>>>

\begin{figure}[tp]
\centering
\includegraphics[width=\textwidth]{figures/2ljets_summary_no_sr_log.png}
\caption[
Alternative summary table with backgrounds fitted to control regions only
]{%
Alternative summary table with backgrounds fitted to control regions only.
A version fitted also to signal regions is shown in
Figure~\ref{fig:2ljets_summary}.
Unlike Figure~\ref{fig:2ljets_summary} the this figure does not adjust its
background estimates to match the observed data in signal regions; notably,
this figure has much larger background predictions in SR-Low-a and SR-Low-b,
with correspondingly larger negative significances in those regions.
The two figures also have aesthetic differences in the colouring and grouping
of background samples.
\\[0.4em]
Fitting to signal regions is the policy of the \atlas\ SUSY group, but deviates
from the intentions of the significance measure.
Because the post-fit yields in SR-Low achieve a small negative significance,
all mentions of its data deficit were removed from the paper.
}
\label{fig:2ljets_summary_no_sr}
\end{figure}
